MS Depression Paper, post replication, started 2022 09 21

### 2023-10-05 Biological_Psychiatry_Revision_Scripts/msdepression_n380_started_20230927_mm_BP_r1.Rmd
add diagnosis*age interaction

@@

>>>>

[x] agexdep to address duration issue: lm(proportion_affected ~ Diagnosis*Age)

  - Age x dep interaction:  (Estimate<0.001, CI -0.003-0.002 , P=0.84)

@@

#Agexdepression interaction - Not significant
diagnosis_by_network_interaction_lm_agexdep <- lm(proportion_affected ~  Diagnosis*PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lm_agexdep)

#Age x dep interaction:  (Estimate<0.001, CI -0.003-0.002 , P=0.84)
confint(diagnosis_by_network_interaction_lm_agexdep)
